\section{Results}
\subsection{Employer Interviews}

\input{figures/themes}
\input{tables/themes}

A total of 20 interviews were conducted with hiring managers at technology companies. While theoretical saturation was achieved after 12 interviews, 8 additional interviews were completed to strengthen the robustness of the findings and address reviewer recommendations. Among the interviewees, 5 were C-level executives, 2 were senior leadership, and the remaining 13 were mid-to-senior-level managers.

Hiring managers were willing to interview various numbers of students. The smallest commitment was 3 interviews (2 hiring managers) and the largest was 10 (1 hiring manager); all the remaining hiring managers (17) were willing to interview 5 students.

When asked about the traits they desired, 7 common themes were identified (Figure~\ref{fig:themesChart}, Table~\ref{tab:themes}):  \textbf{problem solving} (ability to solve complex problems without hand-holding), \textbf{initiative} (solving problems without being asked), \textbf{teamwork/collaboration} (communication and coachability), \textbf{domain knowledge} (specific technologies used at the company), \textbf{curiosity} (learning for the sake of it), \textbf{product sense} (understanding the product and users), and \textbf{persistence} (working until a problem is solved).

\subsection{Student Motivation}

We recruited 650 students to complete the motivation survey; 591 (the control group) did not view the hiring manager agreements, and 59 (the experimental group) did. Students were recruited from juniors and seniors at state-funded universities and community and technical colleges in the US.

Data normality was assessed using the Shapiro--Wilk test for each construct within both groups. The normality assumption was satisfied for all constructs ($p > 0.05$). Data for some constructs were found to violate equal-variance assumptions, so Welch $t$ tests were performed to compare means across groups for each construct. To control for multiple comparisons, $p$ values were adjusted using the Holm--Bonferroni method.

The results (Figures \ref{fig:value} and~\ref{fig:cost} and Table~\ref{tab:stats}) revealed statistically significant differences between students who had and had not viewed the hiring manager agreements across all constructs ($p < 0.01$ to $p < 0.0001$) except Opportunity and Emotional Costs. Effect size analyses indicated a small practical effect for Utility Value; a moderate effect for Intrinsic Value, Effort Cost, and Outside Effort Cost; and a large effect for Attainment Value ($d = 2.17$). All significant differences favored increased motivation among students who viewed the agreements.

\input{figures/value}
\input{figures/cost}
\input{tables/stats}