\begin{floatappendix*}
\caption{Student motivation survey}
\label{tab:motivationSurvey}
\begin{tabular}{llp{11.85cm}c}
\toprule
\multicolumn{2}{l}{\textbf{Construct}} & \textbf{Question (5-point Likert)} & \textbf{Cronbach's $\alpha$} \\ \midrule
\multicolumn{1}{l}{\multirow{7}{*}{\begin{tabular}[c]{@{}l@{}}\textbf{Value}\\ \textbf{\cite{ecclesMindActorStructure1995}}\end{tabular}}} & \multirow{2}{*}{\textbf{Intrinsic}} & In general, I think I would find working on open source projects... & \multirow{2}{*}{0.78} \\ \cmidrule{3-3}
\multicolumn{1}{l}{} &  & How much do you think you would like working on open source projects? &  \\ \cmidrule{2-4} 
\multicolumn{1}{l}{} & \multirow{3}{*}{\textbf{Attainment}} & Is the amount of effort that it would take to do well in open source contributions worthwhile to you? & \multirow{3}{*}{0.73} \\ \cmidrule{3-3}
\multicolumn{1}{l}{} &  & I feel that participating in open source activities is \rule{4em}{0.5pt} to my being a competent engineer. &  \\ \cmidrule{3-3}
\multicolumn{1}{l}{} &  & How important would it be to you to do well in open source work? &  \\ \cmidrule{2-4} 
\multicolumn{1}{l}{} & \multirow{2}{*}{\textbf{Utility}} & How useful do you think it would be to participate in open source work for what you want to do after you graduate? & \multirow{2}{*}{0.58} \\ \cmidrule{3-3}
\multicolumn{1}{l}{} &  & How useful do you think it would be to participate in open source work for your daily life outside school? &  \\ \midrule
\multicolumn{1}{l}{\multirow{10}{*}{ \begin{tabular}[c]{@{}l@{}}\textbf{Cost}\\ \textbf{\cite{flakeMeasuringCostForgotten2015}}\end{tabular}}} & \multirow{3}{*}{\textbf{Effort}} & Participating in open source would take up too much time. & \multirow{3}{*}{0.76} \\ \cmidrule{3-3}
\multicolumn{1}{l}{} &  & I would have to put too much energy into open source work. &  \\ \cmidrule{3-3}
\multicolumn{1}{l}{} &  & Participating in open source work would require too much effort. &  \\ \cmidrule{2-4} 
\multicolumn{1}{l}{} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}\textbf{Outside}\\ \textbf{Effort}\end{tabular}} & I have so many other commitments that I can't put forth the effort needed for open source work. & \multirow{2}{*}{0.7} \\ \cmidrule{3-3}
\multicolumn{1}{l}{} &  & Because of all the other demands on my time, I don't have enough time for open source work. &  \\ \cmidrule{2-4} 
\multicolumn{1}{l}{} & \multirow{2}{*}{\textbf{Opportunity}} & Working on open source work would cause me to miss out on too many things I care about. & \multirow{2}{*}{0.72} \\ \cmidrule{3-3}
\multicolumn{1}{l}{} &  & I wouldn't be able to spend as much time doing the other things that I like to do if I did open source work. &  \\ \cmidrule{2-4} 
\multicolumn{1}{l}{} & \multirow{3}{*}{\textbf{Emotional}} & I would be concerned about being embarassed if my work in open source is inferior to that of my peers. & \multirow{3}{*}{0.74} \\ \cmidrule{3-3}
\multicolumn{1}{l}{} &  & Working on open source work would be emotionally draining. &  \\ \cmidrule{3-3}
\multicolumn{1}{l}{} &  & Working on open source work would be too frustrating. &  \\ \bottomrule
\end{tabular}
\end{floatappendix*}